quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Try to optimize the model
Added langevitour output for both limb layouts

<!-- Assessing which of the 8 NLDR layouts on the PBMC3k data  (shown in @fig-NLDR-variety) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, c, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts b and e, that have small separations between oddly shaped clusters. Layout e is the best choice.-->

@@

## Compute hexbin parameters
num_bins_x_limb <- 16

@@

@@

## Compute hexbin parameters
num_bins_x_limb <- 13

@@

>>>>

<!-- Assessing which of the 8 NLDR layouts on the limb3k data  (shown in @fig-NLDR-variety) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, c, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts b and e, that have small separations between oddly shaped clusters. Layout e is the best choice.-->

@@

## Compute hexbin parameters
num_bins_x_limb <- 25

@@

```{r}
#| label: prep-limb-tsne-author-model-proj

data_limb <- training_data_limb |> 
  select(-ID) |>
  mutate(type = "data")

df_b_limb <- df_bin_limb |>
  dplyr::filter(hb_id %in% df_bin_centroids_limb$hexID) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b_limb <- df_b_limb[match(df_bin_centroids_limb$hexID, df_b_limb$hb_id),] |>
  dplyr::select(-hb_id)

# Apply the scaling
df_model_data_limb <- bind_rows(data_limb, df_b_limb)
scaled_limb <- scale_data_manual(df_model_data_limb, "type") |>
  as_tibble()

scaled_limb_data <- scaled_limb |>
  filter(type == "data") |>
  select(-type)

scaled_limb_data_model <- scaled_limb |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-limb-tsne-author-proj
#| eval: false

# data_limb_n <- data_limb |>
#   select(-type) |>
#   mutate(type = as.character(umap_limb_scaled_with_cluster$cluster))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("data", "model")),
                         levelColors = c("#a65628", "#000000"))
```

@@

## Compute hexbin parameters
num_bins_x_limb <- 19

@@

```{r}
#| label: prep-limb-tsne-best-model-proj

data_limb <- training_data_limb |> 
  select(-ID) |>
  mutate(type = "data")

df_b_limb <- df_bin_limb |>
  dplyr::filter(hb_id %in% df_bin_centroids_limb$hexID) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b_limb <- df_b_limb[match(df_bin_centroids_limb$hexID, df_b_limb$hb_id),] |>
  dplyr::select(-hb_id)

# Apply the scaling
df_model_data_limb <- bind_rows(data_limb, df_b_limb)
scaled_limb <- scale_data_manual(df_model_data_limb, "type") |>
  as_tibble()

scaled_limb_data <- scaled_limb |>
  filter(type == "data") |>
  select(-type)

scaled_limb_data_model <- scaled_limb |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-limb-tsne-best-proj
#| eval: false

# data_limb_n <- data_limb |>
#   select(-type) |>
#   mutate(type = as.character(umap_limb_scaled_with_cluster$cluster))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = distance_df_small_edges_limb$from,
                         lineTo = distance_df_small_edges_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("data", "model")),
                         levelColors = c("#ff7f00", "#000000"))
```
